Staged Abstract Interpreter

### 2018-01-05 paper.tex
outline

2. But closure is still not an efficient enough representation.

@@

Store/set operations (join, update) is expensive. Generate efficient store implementation\cite{liang2014fast}.

@@

For example, k-CFA (k > 0) is naturally a kind of whole program analysis, because 
it need the last k calling contexts. But can we analyze programs (or libraries) separately 
which generate the specialized analysis and leave the k calling contexts as dynamic parameters, 
and then install these contexts when we have the whole program.

Another perspective, programs are data for an abstract interpreter, if we have $n$ programs, then there 
are $n$ stages. Probably we can analyze first $m$ programs, and generate a residual abstract interpreter
waiting for the rest $(n-m)$ programs.

>>>>

2. From a performance perspective, closure is still not an efficient enough representation.

@@

Store/set operations (join, update) is also expensive, generating efficient store implementation\cite{liang2014fast}.

@@

Motivation: one of the challenges of modern static analysis is program usually depends on
large libraries programs\cite{toman_et_al:LIPIcs:2017:7121}. 
Can we analyze programs and libraries separately without losing precision? So that we can 
reduce part of the overhead of repeatedly analyzing libraries for different programs.
Similarly, some static analyzers compute summary for a function or a module, that can be reused
later(Facebook Infer). But to my knowledge, they are mostly context-insensitive or imprecise.

Application: for example, k-CFA (k > 0) is naturally a kind of whole program analysis, because 
it need the last k calling contexts as abstraction. But can we analyze programs (libraries) separately 
which generate the specialized analysis and leave the k calling contexts as dynamic parameters, 
and then install these contexts when we have the whole program.

Another perspective: programs are data for an abstract interpreter, so if we have $n$ programs, 
then there can be $n$ stages. 
Probably we can analyze first $m$ programs, and generate a residual abstract interpreter
waiting for the rest $(n-m)$ programs.
